Reproducing Palmius’ filtering & imputation

### 2018-03-13 implementingBipolar/implementationReport.Rmd
added points to path script and RMD

1. This type of simple imputation works, but is not infallable. It is only as powerful as the downsampling, which I see as a fragile step here. 
2. There are still some bugs I have to work on. I was imputed as being in the Benin at one point (I've never been there), which is either because of time zone differences and mean based downsampling or because longitude and lattitude got mixed up somewhere.

@@

```{r finalmap, echo = F}
u2<- readRDS("imputedPalmius.rds")

>>>>

1. This type of simple imputation works, but is not infallable. It is only as powerful as the downsampling/filtering, which I see as a fragile step here. 
2. There are still some bugs I have to work on. I was imputed as being in the Benin at one point (I've never been there), which is either because of time zone differences and mean based downsampling or because longitude and lattitude got mixed up somewhere.
3. In terms of imputed time periods it performed better than I expected it to. Of the 9764 missing windows it imputed all but 62.

@@

```{r finalmap, echo = F, warning=F,message=F}
u2<- readRDS("imputedPalmius.rds")
